\ttitle

### 2016-02-16 Chapters/CPET_Jaundice.tex
Viva Recommendations:
List of abbreviations
All tables should have units, legends
All values and ranges need defining
Chapter 1
 - More discussion of key RCTs
- Short discussion of etiology
Chapter 2
- Review patient numbers on p63 - pathologies dont add up to total
- Aim and end points must match
- Error in AT numbers in adjuvant therapy table
- P72 Remove unjustifed/unsupported conclusion
- P73 Remove GPS conclusion
Chapter 3 p96 Remove conclusions not based on thesis
Chapter 5-6 - Reduce to more undestandable key issues. All tables need legends. Several irrelevant tables should be removed.

\begin{figure}[htbp]
	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/cpet_oj_scatter_at_bil}
		\caption{$\dot{V}_{O_2}$AT versus serum bilirubin}
		\label{fig:cpet_oj_scatter_at_bil}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/cpet_oj_scatter_peak_bil}
		\caption{$\dot{V}_{O_2}$Peak versus serum bilirubin}
		\label{fig:cpet_oj_scatter_peak_bil}
	\end{subfigure}

@@

@@

Taken together, these results appear to suggest that preoperative biliary drainage and resolution of jaundice are unlikely to improve aerobic capacity and cardiopulmonary physiology in these patients.

>>>>

\begin{figure}[htbp]

@@

	\centering
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/cpet_oj_scatter_at_bil}
		\caption{$\dot{V}_{O_2}$AT versus serum bilirubin}
		\label{fig:cpet_oj_scatter_at_bil}
	\end{subfigure}
	\begin{subfigure}{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{Figures/cpet_oj_scatter_peak_bil}
		\caption{$\dot{V}_{O_2}$Peak versus serum bilirubin}
		\label{fig:cpet_oj_scatter_peak_bil}
	\end{subfigure}

	\begin{flushleft}
		The relationship between serum bilirubin and $\dot{V}_{O_2}$AT was weak (Pearson's $\rho$ = - 0.187, $\rho^2$ = 0.035, p = 0.028). There was no correlation between serum bilirubin and $\dot{V}_{O_2}$Peak (Pearson's $\rho$ = - 0.132, $\rho^2$ = 0.017, p = 0.123)
	\end{flushleft}

@@

%Taken together, these results appear to suggest that preoperative biliary drainage and resolution of jaundice are unlikely to improve aerobic capacity and cardiopulmonary physiology in these patients.
%\todo{Remove this conclusion not based on thesis}
